\documentclass[overlapped]{res}
\newcommand{\latex}{\LaTeX\xspace}
\textwidth=5.6in % increase text width to get smaller right margin
\textheight=10in
\usepackage{placeins}
\usepackage{textgreek}
\usepackage{hyperref}
\addtolength{\topmargin}{-.5in}
%\addtolength{\oddsidemargin}{-.5in}

\begin{document}

\name{Ratan Rai Sur} % the \\[12pt] adds a blank line after name

\address{\href{https://ratanrsur.github.io}{\underline{ratanrsur.github.io}} \\ \href{https://www.github.com/ratanrsur}{\underline{github.com/ratanrsur}}}
\address{\href{mailto:ratan.r.sur@gmail.com}{\underline{ratan.r.sur@gmail.com}} \\ \hfill +1 646 410 6411\\\hfill{}US Citizen}
\begin{resume}


    \section{Experiences}

    {\bf ConsenSys/PegaSys - \href{https://www.github.com/Hyperledger/Besu}{\underline{\em Hyperledger Besu}}} \hfill May 2019 - Present \\
    {\em Blockchain Protocol \& Software Engineer\/} - {\em Java}
    \begin{itemize} \itemsep-2pt
        \item Currently working on implementing Beam Sync, the next generation of syncing algorithms.
        \item
            Implemented World State Trie Pruning, a process necessary to prevent a blockchain client from using an unbounded amount of storage.
        \item
            Contributed to {\em Ethereum\/} 1.x community calls, discussing design of stateless client protocols.
    \end{itemize}

    {\bf Recurse Center} \hfill Sep - Dec 2018 \\
    {\em Participant\/}
    \begin{itemize} \itemsep-2pt
        \item
            Wrote \href{https://www.github.com/ratanrsur/raicoin}{\underline{raicoin}}, a toy cryptocurrency, to learn about blockchain.
            Libraries were used only to manage TCP connections and sign/verify messages. - {\em Scala+Akka}
        \item
            Implemented proof-of-work mining and all consensus-reaching behavior, such as peer discovery and block gossip.
    \end{itemize}

    {\bf Travel} \hfill Nov 2017 - Sep 2018
    \begin{itemize} \itemsep-2pt
        \item
            Lived in Brazil for 5 months learning Portuguese.
        \item
            Spent shorter stints in India, Poland, Germany, France, and Hungary.
    \end{itemize}


    {\bf Microsoft - \href{https://www.github.com/Azure/mmlspark}{\underline{\em Microsoft Machine Learning for Apache Spark}}} \hfill Mar 2016 - Nov 2017
    {\em Software Engineer}
    \begin{itemize} \itemsep-2pt
        \item
            Generated and contributed Java bindings to Microsoft Cognitive Toolkit (CNTK). - {\em C++, Java}
        \item
            Used bindings to create CNTKModel, an Apache Spark Transformer that parallelizes evaluation of trained CNTK deep learning models over Spark clusters. - {\em Scala\/}
        \item
            Helped design Spark image schema specification, something lacking from native Spark.
            After a collaboration with Databricks, the changes were made into a pull request and merged to Spark master. - {\em Scala\/}
        \item
            Prototyped PySpark Tensorflow trained-model evaluation transformer. - {\em Python\/}
    \end{itemize}

    {\bf Machine Learning Self-Study} \hfill Sep - Nov 2015
    \begin{itemize} \itemsep-2pt
        \item
            Self taught and implemented various machine learning algorithms.
            Most notably, feedforward multilayer perceptrons with back propagation and regularization. - {\em Julia}
    \end{itemize}

    %\begin{itemize} \itemsep-2pt
        %\item Sat a 10 and two 7 day silent retreats at Dhamma Giri Vipassana International Academy, India and Insight Meditation Society, Massachusetts respectively.
    %\end{itemize}

    \section{Education}
    The Cooper Union for the Advancement of Science and Art \hfill New York, NY  \\
    Bachelor of Science, Civil Engineering              \hfill Class of 2015 \\
    Full Tuition Merit Scholarship                          \hfill 2011 - 2015

    %{{\bf {\em Tactile City\/}}} \hfill 2015
    %\begin{itemize} \itemsep-2pt
        %\item
            %Prototyped ambience-aware sound systems and collaborated with artists and architects to conceptualize a tactile language for the visually impaired to navigate urban environments. - {\em Python, Electronics\/}
        %\item
            %Presented the proposal to the commissioner of the New York Mayor's Office for People with Disabilities.
        %\item
            %Exhibited the results of the project at the {\em IdeasCity New York} festival.
        %\item
            %Featured in NY1's educational program {\em It Ain't Rocket Science\/}.
    %\end{itemize}

    {\bf {\em HackCooper\/}} \hfill 2014 \& 2015
    \begin{itemize} \itemsep-2pt
        \item
            Organized the first ever hackathons at The Cooper Union.
        \item
            Fund-raised over \$30,000 in sponsorship across the two hackathons.
        %\item
            %Participated in the first hackathon during operational downtime by designing hardware for a sandwich-making robot.
    \end{itemize}

    %{\bf {\em C L O U D S\/}} \hfill Fall 2014 - Spring 2015
    %\begin{itemize} \itemsep-2pt
        %\item Animated electronic displays interfaced with Arduino and Raspberry Pi systems with mathematical visualizations for the artist Yorgo Alexopolous. - {\em C++\/}
    %\end{itemize}

    %{\bf Patent Law for Inventors} \hfill Summer 2012
    %\begin{itemize} \itemsep-2pt
        %\item One of six students invited to a trial summer course in which each student conceived a patentable invention.
        %\item Wrote a provisional patent application for a multi-pour bottle-attachment.
        %\item Presented CAD models of the invention to the president of The Cooper Union.
    %\end{itemize}

    \section{Publications}
        {\bf Massively Parallel Neural Networks with CNTK on Spark} - Microsoft Journal of Applied Research \\
        {\bf \href{https://arxiv.org/pdf/1804.04031.pdf}{\underline{Flexible and Scalable Deep Learning with MMLSpark}}} - Journal of Machine Learning Research

    \section{Languages, Technologies, etc.}
    \begin{itemize} \itemsep-2pt
        \item
            Scala, Rust, Julia, Java, Python, C++, Racket, Haskell
        \item
            Linux/macOS, Bash, git, Spark, Docker, GitHub, Agile, TDD
    \end{itemize}

    \section{Other Experiences}

    {\bf Silent Mindfulness Meditation Retreats} \hfill 2016, 2017

\end{resume}
\end{document}
